An event-sourced and distributed database with IPLD and materialized views

### 2019-09-19 draft.tex
rm var names
Signed-off-by: andrew <andrew@textile.io>

\begin{example*}
\centering
\begin{minipage}{0.7\textwidth}
\begin{lstlisting}
// Log multiaddress
ipel := "/ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab"

// Encapsulated multiaddress
address := "/ip4/127.0.0.1/tcp/1234/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab"

>>>>

\begin{example*}
\centering
\begin{minipage}{0.7\textwidth}
\begin{lstlisting}
// Log multiaddress
 "/ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab"

// Encapsulated multiaddress
 "/ip4/127.0.0.1/tcp/1234/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab"
